Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
rulecolor in snippets
Syntax error.
Shorten section beginning.

\newminted{python}{frame=single}

@@

In this section, we discuss the general principles of the application
programming interface (API) of \sklearn. We first specify the representation of
data and then proceed by describing the core interface of the library.

All objects within \sklearn share a uniform common basic API consisting of three
complementary interfaces: an \textit{estimator} interface for building and
fitting objects, a \textit{predictor} interface for making predictions and a
\textit{transformer} interface for converting data. As much as possible, our
design choices have been guided so as to avoid the proliferation of framework
code. We try to adopt simple conventions and to limit to a minimum the number of
methods an object must implement. The API is designed to adhere to the following
broad principles:

@@

Pipeline([("pca", fu,
          ("feat_sel", SelectKBest(k=100)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}

>>>>

\definecolor{rulecolor}{rgb}{0.80,0.80,0.80}
\newminted{python}{frame=single,rulecolor=\color{rulecolor}}

@@

All objects within \sklearn share a uniform common basic API consisting of three
complementary interfaces: an \textit{estimator} interface for building and
fitting models, a \textit{predictor} interface for making predictions and a
\textit{transformer} interface for converting data. As much as possible, our
design choices have been guided so as to avoid the proliferation of framework
code. We try to adopt simple conventions and to limit to a minimum the number of
methods an object must implement. The API is designed to adhere to the following
broad principles:

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=100)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
